A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-11 doc/draft-01-stokes/04numerical.tex
Adding annulus discretization to pdf
small fix to numerical

\subsubsection{Spurious eigenvalues}
\label{subsec:spurannulus}
As noted in~\cref{subsec:dlanalysis},
if $k_{0}$ is a Neumann eigenvalue corresponding to the interior
inclusion, which in our case is the disk $r\leq r_{1}$, then
$f_{D}(N)(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
is not a Dirichlet eigenvalue of the annulus, i.e.
the integral equation $-\cI - 2\cD_{k} -2\cW$ has a spurious eigenvalue.
In~\cref{fig:spur}, we demonstrate this result and also show that 
$f_{C}^{N}(k_{0}) \neq 0$, i.e., the combined field representation is
robust and invertible at all values of $k$ which are not the Dirichlet
eigenvalues of the annulus.

>>>>

\subsubsection{Spurious eigenvalues}
\label{subsec:spurannulus}
As noted in~\cref{subsec:dlanalysis},
if $k_{0}$ is a Neumann eigenvalue corresponding to the interior
inclusion, which in our case is the disk $r\leq r_{1}$, then
$f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
is not a Dirichlet eigenvalue of the annulus, i.e.
the integral equation $-\cI - 2\cD_{k} -2\cW$ has a spurious eigenvalue.
In~\cref{fig:spur}, we demonstrate this result and also show that 
$f_{C}^{N}(k_{0}) \neq 0$, i.e., the combined field representation is
robust and invertible at all values of $k$ which are not the Dirichlet
eigenvalues of the annulus.
